Binary companions of red giant stars in \apogee\ \DR

### 2018-03-06 paper/1-catalog/twoface-catalog.tex
TODOs

% Notebook: HighK-unimodal-catalog
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-unimodal}
\end{center}
\caption{%
Examples of high-$K$ stars with effectively unimodal posterior samplings and
converged MCMC samplings.
Each panel shows the data (black markers), phase-folded at the period of the
posterior sample with maximum posterior probability.
Visit velocity uncertainties are shown as black error bars (these are typically
smaller than or equal to the size of the markers), and the inferred jitter as
grey, capped error bars.
Line (blue) shows the orbit compute from the posterior sample with maximum
posterior probability.
\label{fig:highK-unimodal}
}
\end{figure}

@@

@@

@@

@@

@@

>>>>

% Notebook: HighK-unimodal-catalog
\begin{figure}[hp]
\begin{center}
\includegraphics[width=\textwidth]{highK-unimodal}
\end{center}
\caption{%
Randomly-selected examples of high-$K$ stars with effectively unimodal posterior
samplings and converged MCMC samplings.
Each panel shows the data (black markers), phase-folded at the period of the
posterior sample with maximum posterior probability.
Visit velocity uncertainties are shown as black error bars (these are typically
smaller than or equal to the size of the markers), and the inferred jitter as
grey, capped error bars.
Line (blue) shows the orbit compute from the posterior sample with maximum
posterior probability.
\label{fig:highK-unimodal}
}
\end{figure}

@@

\todo{also look at trends with Teff?}

\todo{Cite troup, who also noted this}

@@

\todo{Mathieu et al. 2004}

@@

\todo{eccentricity distribution w/ prior over-plotted}

@@

\todo{Interesting companions w/ large M2min, WD/NS/BH companions?}

\todo{Plot: M1 vs. M2min}

\todo{Plot: M2min vs. a2sini}

\subsection{Eclipsing}

\todo{Stars with Kepler light curves}

@@

We don't need to know the orbits of each individual system: that's the power in
this.
